% Created 2021-03-31 Wed 21:09
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[compact]{titlesec}
\usepackage{tgtermes}
\usepackage{helvet}
\titleformat{\section}[block]{\Large\scshape}{}{1em}{}[\titlerule]
\setlength{\parindent}{0em}
\usepackage{enumitem}
\setlist[1]{itemsep=-5pt}
\usepackage[left=1in,right=1in,top=1cm,bottom=1cm]{geometry}
\usepackage{titling}
\setlength{\droptitle}{-10pt}
\posttitle{\par\end{center}}
\makeatletter\def\@maketitle{\begin{center}\textsc{\Huge{\@title}}\end{center}\begin{center}\href{mailto:\emailaddress}{\emailaddress}\hspace{1em}\href{\website}{\website}\end{center}\vspace{-15pt}}\makeatother
\date{}
\newcommand\website{https://matthew.rijalburke.com}
\newcommand\emailaddress{matthew.burke@cantab.net}
\pagenumbering{gobble}
\date{}
\title{Matthew Burke}
\hypersetup{
 pdfauthor={},
 pdftitle={Matthew Burke},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 26.3 (Org mode 9.1.9)}, 
 pdflang={English}}
\begin{document}

\maketitle

\section*{Education}

\subsection*{Macquarie University, Sydney}

Doctor of Philosophy in Mathematics 2011-2015

\subsection*{Christ's College, University of Cambridge}

Part III Mathematics (MMATH) 2010-2011

Bachelor's degree in Mathematics (BA) 2007-2010 

\section*{Work experience}

\subsection*{Jan 2020 - Present: Lyryx Learning}

Senior software developer (11 months); Director of technology (Current)

\begin{itemize}
\item Designed, developed and distributed a cross-platform mobile and web application to combine existing textbook content with new interactive questions. Used TypeScript, SQLite and Capacitor.
\item Created a local development environment for an existing Java web application. Used Docker, NGINX and Firejail to locally develop features that spanned multiple production servers.
\item Constructed a Web API for automatically scheduling examinations. Used Java Servlets and MySQL.
\end{itemize}

\subsection*{Aug 2019: Cybera Data Science Fellowship}

Data science fellow

\begin{itemize}
\item Collaborated with an industry partner to clean, explore and analyse 7 years of live events data stored in a PostgreSQL database with over 13 million entries.
\item Constructed a generalised linear model (GLM) for analysing count data and a log linear model for analysing sales data. Used Python scripts, Jupyter notebooks and the R programming language.
\end{itemize}

\subsection*{Sep 2017-Sep 2019: University of Calgary}

Postdoctoral scholar

\begin{itemize}
\item Designed and completed projects in pure mathematics and computer science leading to a publication in a peer-reviewed journal and another paper under review.
\item Created a formal proof of a well-known result in category theory using the Coq proof assistant.
\item Provided mentoring support for two PhD students and reviewed two papers for mathematics journals.
\item Organised the University of Calgary Peripatetic Seminar (Dec 2017-May 2019) and chaired a session of the Alberta Mathematics Dialogue 2018.
\item Used Jupyter notebooks to lecture 4 classes of around 230 students each.
\end{itemize}

\subsection*{Jun 2016-Aug 2017: MathSpire Ltd.}

Software engineer (5 months); Chief technology officer (9 months)

\begin{itemize}
\item Developed a cross-platform mobile and desktop application to teach A-level mathematics using interactive graphs, videos and integrated testing. Used F\#, .NET and Xamarin.
\item Created a web front-end and API for teachers to track student progress.
\item Showcased the application at the BETT education technology conference.
\end{itemize}

\section*{Projects}

\begin{itemize}
\item \textbf{Fog of war chess:} (\url{https://github.com/mwpb/fowc}) Library to play a variant of chess in which the players can only see squares to which they can move. Proof of concept at \href{https:fogofwarchess.com}{fogofwarchess.com}.
\item \textbf{Advent of code:} (\url{https://github.com/mwpb/adventOfCode2019}) Java solutions to all problems in the 2019 advent of code.
%\item \textbf{Colimits in Coq:} (\href{https://github.com/mwpb/postulated-colimits-in-coq}{https://github.com/mwpb/postulated-colimits-in-coq}) Computer verification of a result in category theory using the coq proof assistant.
\item \textbf{Cryptopals challenges:} (\url{https://github.com/mwpb/matasano-go}) Solutions written in Go. First three sets completed.
%\item \textbf{Kaggle Box Office Predictions:} (\url{https://github.com/mwpb/kaggle-projects}) Competition to predict the revenue of films. Uses IPython and Google Colab.
\end{itemize}

\section*{Publications}

\begin{itemize}
  \item Tangent infinity-categories and Goodwillie calculus, \emph{Memoirs of the American Mathematical Society}, to appear.
  \item A Synthetic Version of Lie's Second Theorem, \emph{Applied Categorical Structures}, 2018.02.06. Available at \url{https://doi.org/10.1007/s10485-018-9518-2}.
  \item Connected Lie Groupoids are Internally Connected and Integral Complete in Synthetic Differential Geometry, \emph{Symmetry, Integrability and Geometry: Methods and Applications}, 2016.06.29. Available at \url{http://www.emis.de/journals/SIGMA/2017/007/}.
\end{itemize}

\end{document}
